quollr: An R Package for Visualizing 2D Models from Nonlinear Dimension Reductions in High Dimensional Space

### 2024-06-07 paper-quollr.Rmd
Fit an appropriate model for the prism data
Added scratch details about what I learnt from the model

@@

@@

>>>>

### Construct model in $2\text{-}D$

@@

### Lifting the model into $p\text{-}D$

@@

What can I see in high-D?

- Four clusters that are really close

What can I see in 2D layout?

- Several clusters (more that what see in high-D)

What can learn from the model?

- There are four clusters, but not as the same cluster what data shows. In 2D, the two of actual clusters (high-D clusters) are really close. Also, one of the big high-D cluster is separated to two sub clusters.
